Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
explicitly note that 15 AV subjects is subgroup

\subsection{Participants}
% AD study
In the audio-description study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior audio-description study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the block-design localizer study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all studies, participants received monetary compensation and gave written
informed consent for their participation and for public sharing of obtained data
in anonymized form. The studies had prior approval by the Ethics Committee of
Otto-von-Guericke University of Magdeburg, Germany.

>>>>

\subsection{Participants}
% AD study
In the audio-description study \citep{hanke2014audiomovie}, 20 German native
speakers (all right-handed, age 21–38 years, mean age 26.6 years, 12 male)
listened to the German audio-description \citep{ForrestGumpGermanAD} of the
movie ``Forrest Gump'' \citep{ForrestGumpMovie}.
% AV study
In the movie study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female), a subgroup of the prior audio-description study,
watched the audio-visual movie with dubbed German audio track
\citep{ForrestGumpDVD}.
% VIS study
In the block-design localizer study \citep{sengupta2016extension}, the same 15
participants took part in a six-category block-design visual localizer.
% participants' health
All participants reported to have normal hearing, normal or corrected-to-normal
vision, and no known history of neurological disorders.
% compensation, consent and shit
In all studies, participants received monetary compensation and gave written
informed consent for their participation and for public sharing of obtained data
in anonymized form. The studies had prior approval by the Ethics Committee of
Otto-von-Guericke University of Magdeburg, Germany.
